---
title: "P8130_hw2"
author: "Shan Jiang"
date: "9/24/2018"
output: html_document
---
## Prolem 6(a)
* Import Data from xlsx file and detect the NAs in the data
```{r 1.1.1}
library(tidyverse)
Migraine <- readxl::read_excel("~/Downloads/CUMC Y1/Biostat Method/Hw 2/Migraine.xlsx")
any(is.na(Migraine))
nrow(Migraine)
```

* Find out the NAs in each column and Rename the dataframe
```{r 1.1.2}
Migraine_NA = Migraine
sum(is.na(Migraine_NA))
colSums(is.na(Migraine_NA))
```


* Removing NAs in R dataframes
```{r 1.1.3}
Migraine_clean = na.omit(Migraine_NA)
View(Migraine_clean)
nrow(Migraine_clean)
colSums(is.na(Migraine_clean))
```
 
* Exploring the dataframe after data cleaning
```{r 1.1.4}
names(Migraine_clean)
head(Migraine_clean)
tail(Migraine_clean)
```
Rename the data.frame
```{r 1.1.5}
Migraine_df = na.omit(Migraine_NA)
View(Migraine_df)
```

* Sum the data with name  
```{r 1.1.6}
library(psych)
describeBy(Migraine_df, Migraine_df$Migraine)

describeBy(Migraine_df, Migraine_df$CESD >= 16)
describeBy(Migraine_df$NDDIE, Migraine_df$CESD >= 16)
```
* Sum the data by cutoff of NDDIE >= 16
```{r 1.1.9}
describeBy(Migraine_df, Migraine_df$NDDIE >= 16)
```


*Boxplot of CESD by migraine status
```{r 1.2.1}
  boxplot(Migraine_df$CESD~Migraine_df$Migraine,
        main = "Boxplot of CESD by migraine status "
        )
```
*Boxplot of NDDIE by migraine status
```{r 1.2.2}
boxplot(Migraine_df$NDDIE~Migraine_df$Migraine,
        main = "Boxplot of NDDIE  by migraine status "
        )
```

ABNAS (the sum of memory and language)
```{r 1.2.3}
boxplot(Migraine_df$`ABNAS memory`~Migraine_df$Migraine,
        main = "Boxplot of ABNAS memory by migraine status "
        )
boxplot(Migraine_df$`ABNAS language`~Migraine_df$Migraine,
        main = "Boxplot of ABNAS language by migraine status "
        )
```
In this graph, we can see 




```{r}
library(gmodels)
apply(Migraine_df, 2, mean)
colMeans(Migraine_df)
mean_df <- aggregate(Migraine_df, by = list(Migraine_df$Migraine), mean)
sd_df <- aggregate(Migraine_df, by = list(Migraine_df$Migraine), sd)

quantile(Migraine_df$CESD)
quantile(Migraine_df$NDDIE)
quantile(Migraine_df$`ABNAS memory`)
quantile(Migraine_df$`ABNAS language`)
 
```

 mean(Migraine_df$CESD)
mean(Migraine_df$NDDIE)
mean(Migraine_df$`ABNAS memory`)
mean(Migraine_df$`ABNAS language`)

sum(Migraine_df$`ABNAS memory`, Migraine_df$`ABNAS language`)


